Maximum Entropy Spectral Analysis: a case study

### 2021-03-10 paper/mesa.tex
Removed merge strings

\begin{itemize}
\item \textbf{Final prediction Error } 
The first criterion is due to Akaike~\cite{Akaike1970StatisticalPI}. He proposed that $m$ should be chosen as the 
length that minimises the error when the filter is used as a predictor, the \emph{final prediction} error (FPE): 
\begin{equation}
    FPE(m) = \mathbb{E}\left[ \left((x_t - \hat x_t) ^ 2\right) \right]
\end{equation}
with $\hat{x}_t = \sum_{i = 1}^M a_i x_{t - i}$.
Minimizing FPE is equivalent to minimizing the quantity: 
\begin{equation}
    \mathcal{L}_{\rm FPE}(m) = P_{m} \frac{N + m + 1}{N - m - 1}
\end{equation}
with $P_m$ defined by the prediction error filter equation \sschmidt{What is this equation?}.
\wdp{comment on N that goes to infinity, just minimising the variance of the process}
\item \textbf{Criterion Autoregressive Transfer function (CAT)}
This second loss function is due to Parzen~\cite{bhansali1986}, and it is defined as
\begin{equation}
    \mathcal{L}_{\rm CAT}(m) = \frac{1}{N}\sum_{k = 1}^m \frac{N - k}{N P_k} - \frac{N - m}{N P_m}.
\end{equation}
It has the interesting property that the distance between the original filter and the estimate is minimum and asymptotically unbiased. \wdp{please expand}

\item \textbf{Optimum Bayes Decision rule} 
The last criterion we will consider is the Optimum Bayes Decision rule (OBD)\cite{doi:10.1029/WR018i004p01097}. With the technique of asymptotic integration, the loss function is proposed to be the length that maximizes the posterior distribution \sschmidt{Which posterior?}, \wdp{please check this equation}: 
   \begin{align}
        \mathcal{L}_{\rm OBD}&(m) = (N - m - 2) \log(P_m) \nonumber\\
        &+ m \log(N) + \sum_{k = 0}^{m-1} \log(P_k) + \sum_{k = 1}^{m} a_k^2\,.
    \end{align}
\end{itemize}

Once a loss function is selected, the choice of the best recursion order is straightforward: we solve the Levinson\wdp{add ref} recursion until $M_{max}$, as given in Eq.~\ref{eq:MMAx}, iterations are reached. Then, the order $m$ is selected to be the one that minimizes the loss function.

@@

its easily shown that $S(f)^{-1}$ can be written as a Fourier Expansion in terms of some $\lambda$s coefficients. THe determination of the values for the $\lambda$s uniquely solve the problem of power-spectral density estimation. Some properties for the coefficients can be worked out easily. First, since $S(f)$ is positive definite the $\lambda$s coefficient show the property 

>>>>

\begin{itemize}
\item \textbf{Final prediction Error } 
The first criterion is due to Akaike~\cite{Akaike1970StatisticalPI}. He proposed that $m$ should be chosen as the 
length that minimises the error when the filter is used as a predictor, the \emph{final prediction} error (FPE): 
\begin{equation}
    FPE(m) = \mathbb{E}\left[ \left((x_t - \hat x_t) ^ 2\right) \right]
\end{equation}
with $\hat{x}_t = \sum_{i = 1}^M a_i x_{t - i}$.
Minimizing FPE is equivalent to minimizing the quantity: 
\begin{equation}
    \mathcal{L}_{\rm FPE}(m) = P_{m} \frac{N + m + 1}{N - m - 1}
\end{equation}
with $P_m$ defined by the prediction error filter equation \ref{eq:errorFilter1}. \\ 
If the $N \to \infty$ limit is considered,remembering $m_{max} = 2N / \log(2N)$, we see that N dominates both the numerator and the denominator of the fraction: in large $N$ limit using Akaike's loss function is equivalent to the minimization of the variance $P_m$ of the process.

\item \textbf{Criterion Autoregressive Transfer function (CAT)}
This second loss function has been written by Parzen and studied into details by Banshali ~\cite{bhansali1986}. 
It is based on the assumption that the observed process is an infinite order autoregressive process 
\begin{equation} 
x_t = \sum_{i = 1}^{\infty}a_{i}x_{t-i} + \nu_t
\end{equation} 
and tries to select the order $m$ as the best finite-order approximation for the observed process. Being N the number of samples it has the property that $m \to \infty$ as $N \to \infty$. Since any real-valued stochastic process can be written as a ARMA(p,q) process (Wold theorem) i.e. an $AR(\infty)$ process, this is a physically significant property. 
The loss function has the functional form: 
\begin{equation}
    \mathcal{L}_{\rm CAT}(m) = \frac{1}{N}\sum_{k = 1}^m \frac{N - k}{N P_k} - \frac{N - m}{N P_m},
\end{equation}
and the so chosen order is found to be asymptotically unbiased for $P_N$.

\item \textbf{Optimum Bayes Decision rule} 
The last criterion we will consider is the Optimum Bayes Decision rule (OBD)\cite{doi:10.1029/WR018i004p01097}. Let $x(t)$ be the observed 
time series for the process that has to be described as an autoregressive process of order $m$ (AR(m)) with m to be determined. The OBD is obtained chosing between M different hypothesis $H_i, i = 1, \dots, M$ maximizing their posterior distribution $P(H_i\vert x(t))$. Each
hypothesis is uniquely determined from both the length and the values of the filter under study. Chosing a Likelihood of the form \ref{eq:p_forecast} and uniform priors for both the coefficients and the hypothesis Rao has shown that chosing the minimum for $-log(P(H_i \vert x(t))$, i.e. maximizing the posterior for $H_i$, is asymptotically equivalent to the minimization of \wdp{please check this equation}:

   \begin{align}
        \mathcal{L}_{\rm OBD}&(m) = (N - m - 2) \log(P_m) \nonumber\\
        &+ m \log(N) + \sum_{k = 0}^{m-1} \log(P_k) + \sum_{k = 1}^{m} a_k^2\,.
    \end{align}
\end{itemize}

Once a loss function is selected, the choice of the best recursion order is straightforward: we solve the Levinson \cite{doi:10.1002/sapm1946251261} recursion until $M_{max}$, as given in Eq.~\ref{eq:MMAx}, iterations are reached. Then, the order $m$ is selected to be the one that minimizes the loss function.

@@

its easily shown that $S(f)^{-1}$ can be written as a Fourier Expansion in terms of some $\lambda$s coefficients. The determination of the values for the $\lambda$s uniquely solve the problem of power-spectral density estimation. Some properties for the coefficients can be worked out easily. First, since $S(f)$ is positive definite the $\lambda$s coefficient show the property 
